A Technique for Inter-Retailer Recommendations

### 2014-06-11 paper2/paper.tex
Edits...
Restructure Baselines subsection.

\title{A Technique for Inter-Catalogue Recommendations}
\author{Bill Chickering and Jamie Irvine\\
CS 399 with Anand Rajaraman\\
Stanford University}
\renewcommand{\today}{June 11, 2014}
\maketitle

@@

\subsection*{\em LatentFeatureRecommender}
Although the $NeighborhoodRecommender$ leverages the information contained in
the recommendation graphs to some extent, it is still primarily based on product
descriptions. Presumably, the graphs are derivative of a collaborative filtering
scheme, and hence, reveal associations between products that are not evident
from the language of their descriptions. For example, a dress's description
might not capture if it is more conservative or more risque. Yet, this could be
the salient feature it has in common with an associated recommendation.  These
sort of abstract, perhaps ineffable, features can be essential to item-item
relations. We must therefore ask whether we can more fully utilize the given
graphical information to discover these latent features in order to choose
better inter-catalogue associations.

@@

\section*{Performance}
\subsection*{Baselines}
To understand how well our LSI recommender performs, we need good baselines
for comparison.  The simplest and easiest to beat baseline is the Random 
Recommender. This recommender randomly picks pairs of products, one from 
each catalogue, and recommends them together. This should obviously be the 
worst performing recommender but it gives us some sense of whether we are 
doing anything intelligent in our choices of recommendation.

A more impressive baseline is that of the Simple Content-Based approach, 
outlined earlier in the paper. This recommender uses information exclusively
from the descriptions of the products and ignores the recommendation graphs 
entirely. A third, somewhat similar baseline comes from the Neighborhood 
Content-based variant, which looks at the content similarity between 
neighborhoods of products.

We construct a couple of other baselines to show that our performance is not
exclusively due to any single feature of the recommender. One such baseline
tests the effects of popularity alone. Incorporating popularity has a large 
impact on the performance of any recommender and part of this is due simply 
to the evaluation metric. Any time we connect to a popular product, we are 
now two away from many more products, increasing the likelihood of getting a
correct recommendation by the 2-precision standard. To ensure that these kinds 
of effects are not the sole reason that our recommender performs well, 
we construct the Popularity Recommender. This recommender simply recommends 
that every product in one catalogue be connected to the two most popular 
products from the other catalogue. This baseline shows how much of the LSI 
recommender's performance is due simply to leveraging popularity and how 
much is due to other factors, such as intelligently learning and mapping 
latent concepts.

It is also informative to test the efficacy of the concept mapping, since this
such a hard task. As in product-product content-similarity, it is difficult to
capture similarity using descriptions alone. It is not even clear that a mapping 
necessarily exists between two seperately learned concept spaces. The concepts 
may represent fundamentally different things, which cannot be well mapped to 
each other. We can measure the efficacy of the mapping by comparing it to a 
couple of baselines.

The first baseline is in fact an upper bound of sorts on the mapping. This
baseline recommender is called the One Model Recommender. Unlike the other
baselines, this recommender is not a valid one, as it cheats by using
information from the unpartitioned graph. The One Model Recommender learns a
latent concept space over the entire recommendation graph by allowing the random
walkers to traverse it before it is partitioned. In every other respect, it is
the same as the LSI Recommender. However, since products from both catalogues
are represented in the same concept space, there is no need for a mapping
between concept spaces.

The second mapping-related baseline is the Random Mapper Recommender. As the
name suggests, this recommender is identical to the LSI Recommender, except that
it uses a randomly generated linear transformation to map between concept
spaces. These two baselines represent (not strict) upper and lower bounds on how
well the concept mapping performs. The results show how much of a bottleneck
this step is.

>>>>

\title{A Technique for Inter-Retailer Recommendations}
\author{Bill Chickering and Jamie Irvine\\
CS 399 with Anand Rajaraman\\
Stanford University}
\renewcommand{\today}{June 11, 2014}
\maketitle

@@

\subsection*{\em LatentFeatureRecommender}
Although the $NeighborhoodRecommender$ leverages the information contained in
the recommendation graphs to some extent, it is still primarily based on product
descriptions. Presumably, the graphs are derivative of a collaborative filtering
scheme, and hence, reveal associations between products that are not evident
from the language of their descriptions. For example, a dress's description
might not capture if it is more conservative or more risque. Yet, this could be
the salient feature it has in common with an associated recommendation.  These
sort of abstract, perhaps ineffable, features can be essential to item-item
relations. We must therefore ask whether we can more fully utilize the given
graphical information to discover these latent features in order to choose
better inter-catalogue recommendations.

@@

\section*{Performance}
\subsection*{Baselines}
In addition to the $ContentBasedRecommender$ and the $NeighborhoodRecommender$,
we constructed and tested several other baseline algorithms to compare the
$LatentFeatureRecommender$ against. These baselines show that the performance of
$LatentFeatureRecommender$ is not due to a single mechanism but rather is the
result of the mult-stage algorithm. In this section, we briefly outline these
additional baselines.

\subsubsection*{\em RandomRecommender}
The simplest and least challenging baseline. This recommender randomly chooses a
fixed number of recommendations for each item across catalogues.

\subsubsection*{\em PopularityRecommender}
A baseline that exclusively exploits popularity $\rho$, without any other
knowledge of the recommendation graphs or of item content. This recommender
simply chooses, at random, one of the top three most popular items from the
other catalogue as recommendations for each item in a catalogue. This baseline
aims to demonstrate the efficacy of popularity alone.

\subsubsection*{\em RandomMapRecommender}
This is the $LatentFeatureRecommender$ without the mapping stage. Instead it
generates a random value between -1.0 and 1.0 for each element of the mapping
matrix $A$. As such, it is still leveraging popularity $\rho$ in the same way as
the $LatentFeatureRecommender$. This baseline aims to reveal the importance of
the mapping stage.

\subsubsection*{\em OneModelRecommender}
This is not baseline but rather a cheat. This is the $LatentFeatureRecommender$
except, for this experiment, we defer the graph partitioning until after we have
performed our random walks and constructed a single concept space. Only then do
we partition the items such that their latent feature vectors represent all
items in a single concept space. The goal of this experiment is to determine how
well our algorithm might do if a perfect concept mapping existed and we could
somehow compute it.

%Incorporating popularity has a large impact on the performance of any
%recommender and part of this is due simply to the evaluation metric. Any time we
%connect to a popular product, we are now two away from many more products,
%increasing the likelihood of getting a correct recommendation by the 2-precision
%standard. To ensure that these kinds of effects are not the sole reason that our
%recommender performs well, we construct the Popularity Recommender. This
%recommender simply recommends that every product in one catalogue be connected
%to the two most popular products from the other catalogue. This baseline shows
%how much of the LSI recommender's performance is due simply to leveraging
%popularity and how much is due to other factors, such as intelligently learning
%and mapping latent concepts.
